Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-09-11 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Gleason}
\label{sec:Gleason}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Gleason}

\label{sec:Gleason}

While the finite-precision extension of Kochen-Specker theorem asserts
the non-existence of certain QIVPMs, we also want to understand what
a QIVPM can be when it exists. In Sec.~\ref{sec:Interval-Uncertainty},
the only non-trivial QIVPM~ $\bar{\mu}_{3}$ is induced by the quantum
probability measure~$\mu_{1}$ defined in Sec.~\ref{sec:fuzzy}.
In this section, we first generalize this result, and then show general
QIVPMs may not be induced by any classical IVPM, i.e., no state is
consistent with these kind of QIVPMs.

When we induce $\bar{\mu}_{3}$ by $\mu_{1}$ in Sec.~\ref{sec:Interval-Uncertainty},
we replace $0$ and $0.5$ by $\left[0,0\right]$ and $\left[0.5,0.5\right]$
which are essentially the same as the replaced real numbers. In general,
if we carefully pick a set of overlapping intervals, we can replace
the numbers by the interval containing it. For example, consider the
following collection of intervals: 
\begin{eqnarray}
\widehat{\mathscr{I}}_{n} & = & \set{\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\nonumber \\
 &  & \cup\{\imposs,\necess\}
\end{eqnarray}
which are overlapping intervals with length~$1/n$ except the intervals
at length~$\left(2n\right)^{-1}$ at each end. Then, any state~$\rho$
on a three-dimensional Hilbert space can induce a QIVPM over the intervals
above as follows. We first define a map $\widehat{\iota}_{n}$ from
the interval $[0,1]$ to the collection of intervals as: 
\begin{itemize}
\item when $x=0$ or $x=1$, $\widehat{\iota}_{n}\left(x\right)=\left[x,x\right]$; 
\item when $0<x<1$, $\widehat{\iota}_{n}\left(x\right)=\left[\frac{k-1}{2n},\frac{k+1}{2n}\right]\cap\left[0,1\right]$,
where $k$ is defined by one of the following: 
\begin{enumerate}
\item $k$ even and $\frac{k-0.5}{2n}\le x\le\frac{k+0.5}{2n}$; 
\item $k$ odd and $\frac{k-0.5}{2n}<x<\frac{k+0.5}{2n}$. 
\end{enumerate}
\end{itemize}
It is now not difficult to verify that $\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$
is a QIVPM. For example, consider $n=2$, 
\begin{eqnarray}
\widehat{\mathscr{I}}_{1} & = & \set{\left[\frac{k-1}{4},\frac{k+1}{4}\right]\cap\left[0,1\right]}{k=0,\ldots,4}\cup\{\imposs,\necess\}\nonumber \\
 & = & \{\imposs,\left[0,\frac{1}{4}\right],\left[0,\frac{1}{2}\right],\left[\frac{1}{4},\frac{3}{4}\right],\left[\frac{1}{2},1\right],\left[\frac{1}{4},1\right],\necess\}\,.
\end{eqnarray}
\begin{table}
\caption{\label{tab:Compute-the-QIVPM}Compute the QIVPM~$\widehat{\iota}_{2}\circ\mu_{1}$
from $\mu_{1}$}
\end{table}
Then, $\widehat{\iota}_{2}\circ\mu_{1}$, the QIVPM induced by $\mu_{1}$,
can be computed by Table~\ref{tab:Compute-the-QIVPM}.

\yutsung{Clean up until here.}
